Toward Automatic Translation from OpenACC to OpenMP 4

### 2016-04-20 sig-alternate-sample.tex
added draft

\documentclass{sig-alternate-05-2015}
\usepackage{xcolor}
\newcommand\todo[1]{\textcolor{red}{#1}}

@@

\section{Translation}
\subsection{Tool for Translation}
\todo{1 page including screenshot(s) - description of our tool: what directives it handles, how it works, where to get it - Nawrin}
\subsection{Algorithm}
\todo{0.5 page - description of the conversion algorithm (what clauses translate to what?) - Nawrin/Dr.Overbey} 
\section{Evaluation}
\subsection{Test Corpus}
\subsection{Performance}
\todo{1 page including tables - evaluation: what code did we test it on; how many lines changed; what performance numbers did we get - Nawrin}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
%Appendix A
%\section{Headings in Appendices}
%The rules about hierarchical headings discussed above for
%the body of the article are different in the appendices.
%In the \textbf{appendix} environment, the command
%\textbf{section} is used to
%indicate the start of each Appendix, with alphabetic order
%designation (i.e. the first is A, the second B, etc.) and
%a title (if you include one).  So, if you need
%hierarchical structure
%\textit{within} an Appendix, start with \textbf{subsection} as the
%highest level. Here is an outline of the body of this
%document in Appendix-appropriate form:
%\subsection{Introduction}
%\subsection{The Body of the Paper}
%\subsubsection{Type Changes and  Special Characters}
%\subsubsection{Math Equations}
%\paragraph{Inline (In-text) Equations}
%\paragraph{Display Equations}
%\subsubsection{Citations}
%\subsubsection{Tables}
%\subsubsection{Figures}
%\subsubsection{Theorem-like Constructs}
%\subsubsection*{A Caveat for the \TeX\ Expert}
%\subsection{Conclusions}
%\subsection{Acknowledgments}
%\subsection{Additional Authors}
%This section is inserted by \LaTeX; you do not insert it.
%You just add the names and information in the
%\texttt{{\char'134}additionalauthors} command at the start
%of the document.
%\subsection{References}
%Generated by bibtex from your ~.bib file.  Run latex,
%then bibtex, then latex twice (to resolve references)
%to create the ~.bbl file.  Insert that ~.bbl file into
%the .tex source file and comment out
%the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
%\section{More Help for the Hardy}
%The sig-alternate.cls file itself is chock-full of succinct
%and helpful comments.  If you consider yourself a moderately
%experienced to expert user of \LaTeX, you may find reading
%it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage{xcolor}
\usepackage{xspace}
\newcommand\todo[1]{\textcolor{red}{** #1}}
\newcommand{\pooda}{\textsc{POOD}\xspace}

\newcommand{\pood}{\textsc{Porting OpenACC To OpenMP Directives}\xspace}

\newcommand{\squishlist}{
    \begin{list}{$\bullet$}
     { \setlength{\itemsep}{0pt}      \setlength{\parsep}{3pt}
       \setlength{\topsep}{3pt}       \setlength{\partopsep}{0pt}
       \setlength{\leftmargin}{1.5em} \setlength{\labelwidth}{1em}
       \setlength{\labelsep}{0.5em} } }

@@

\section{Translation}
\todo{1 page including screenshot(s) - description of our tool: what directives it handles, how it works, where to get it - Nawrin}
The major compilers supporting OpenACC are Portland Group (PGI), Cray, and CAPS. On the other hand, Intel has decided not to support OpenACC until accelerators are fully integrated into OpenMP. We describe an automated approach to assist programmers in converting OpenACC to OpenMP, so that same syntax could be used for both Cray and Intel compiler while maintaining the performance. We describe a refactoring (POOD) for this purpose.

\subsection{Translation Tool}
We prototyped the refactoring in a PLDT OpenACC Eclipse plug-in (C analyses and refactorings for OpenACC). Our tool support various data flow analyses, dependence analysis, refactorings, and parser for OpenACC directives. It provides an user interface (UI) for refactorings. Other than UI, it also supports command line interface (CLI), so one can run the refactorings outside Eclipse.

Our tool does not handle all the OpenACC directives. We transformed the directives present in EPCC level 1 OpenACC benchmark except ``kernel" directive. When user invoke a refactoring on a C source file, refactoring engine performs the precondition checking. If preconditions are violated, it shows appropriate error message to user. Then analyses and source translations are executed.

\subsection{Porting OpenACC To OpenMP Directives (POOD)}
The \pood refactoring converts OpenACC directives to OpenMP 4.0 directives.

\textbf{Motivation:} While porting OpenACC to OpenMP it is necessary for directives to be compatible. Without automated tooling, a programmer has to manually transform each directives.

\textbf{Precondition:} A programmer selects a C source file and invokes the \pooda transformation. The following precondition is checked:

\begin{itemize}
\item Source file contains OpenACC directives.
\item OpenACC directives in source code supported by our transformation tool.
\end{itemize}

\textbf{Mechanism:} 
\subsection{Algorithm}
\todo{0.5 page - description of the conversion algorithm (what clauses translate to what?) - Nawrin/Dr.Overbey} 
\section{Evaluation}
\todo{1 page including tables - evaluation: what code did we test it on; how many lines changed; what performance numbers did we get - Nawrin}
\subsection{Test Corpus}
\subsection{Performance}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
\end{document}
